Communicating causal effect heterogeneity

### 2024-07-05 index.qmd
improved p_rope ridgelines

p_rope_densities <- post1_samples_rope |> 
  ggplot() + 
  stat_slab(
    aes(y = factor(.draw), xdist = dist_valence, fill = after_stat(-0.1 < x & x < 0.1)),
    color = valence_dist_samples_color,
    alpha = 0.5,
    scale = 2.5,
    linewidth = 0.5
  ) +
  annotate("text", 
    x = -0.1, y = I(0),
    label = "−ε",
    color = desc_color, 
    vjust = 1.15, 
    fontface = "bold", 
    size = 3
  ) +
  annotate("text", 
    x = 0.1, y = I(0),
    label = "+ε", 
    color = desc_color, 
    vjust = 1.15, 
    fontface = "bold", 
    size = 3
  ) +
  geom_vline(xintercept = c(-0.1, 0.1), zero_color, alpha = 0.1, linetype = "22") +
  scale_fill_manual(values = c("TRUE" = desc_color, "FALSE" = alpha(valence_dist_samples_color, 0.3))) +
  guides(fill = "none") +
  coord_cartesian(clip = "off") +
  scale_x_valence() +
  scale_y_discrete(labels = NULL) +
  theme(
    axis.ticks.y = element_blank(),
    plot.title.position = "plot"
  ) +
  ylab("Posterior draw") +
  xlab("Valence effect") +
  labs(subtitle = "A. PDFs of heterogeneity distributions")

>>>>

p_rope_densities <- post1_samples_rope |> 
  ggplot() + 
  stat_slab(
    aes(y = factor(.draw), xdist = dist_valence, fill = after_stat(-0.1 < x & x < 0.1)),
    color = "gray90",
    # alpha = 0.5,
    scale = 2.5,
    linewidth = 0.5
  ) +
  annotate("text", 
    x = -0.1, y = I(0),
    label = "−ε",
    color = desc_color, 
    vjust = 1.15, 
    fontface = "bold", 
    size = 3
  ) +
  annotate("text", 
    x = 0.1, y = I(0),
    label = "+ε", 
    color = desc_color, 
    vjust = 1.15, 
    fontface = "bold", 
    size = 3
  ) +
  geom_vline(xintercept = c(-0.1, 0.1), zero_color, alpha = 0.1, linetype = "22") +
  scale_fill_manual(values = c("TRUE" = colorspace::lighten(desc_color, 0.35, space = "HLS"), "FALSE" = "gray75")) +
  guides(fill = "none") +
  coord_cartesian(clip = "off") +
  scale_x_valence() +
  scale_y_discrete(labels = NULL) +
  theme(
    axis.ticks.y = element_blank(),
    plot.title.position = "plot"
  ) +
  ylab("Posterior draw") +
  xlab("Valence effect") +
  labs(subtitle = "A. PDFs of heterogeneity distributions")
